Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex
minor fix

\section{Stochastic Regular Expressions}
\label{sec:sre}
To characterize the likely lenses, we must compute the expected number of bits
needed to recover a string in one data source from a synchronized string in the
other data source. To do this, we must first develop a probabilistic langauge
model for our language. We do this with \emph{stochastic regular expressions},
regular expressions annotated with probability information. With this, we can
jointly express a language and a probability distribution over that language. In
the following grammar, $\String$ ranges over strings, and $\Probability$ ranges
over real numbers between 0 and 1, exclusive.

@@

An atom lens \AtomLens{} is merely the iteration of a symmetric DNF Lens.

@@

\paragraph*{Information-Theoretic Cost Metric}
Now that we've developed symmetric DNF lenses, it's important to develop a means
to guage how bijective the lens is.

Instead of searching for \emph{any} term that satisfies the specification, we
search for the \emph{best} term that satisfies the specification. This begs the
question: what metric should we use to determine which term is best?
Intuitively, we aim to synthesize the lens which is ``closest'' to being a
bijection. Somewhat more formally, we aim to synthesize a lens which minimizes
the expected number of bits which must be used to recover the source from the
target, and the target from the source.

>>>>

\section{Stochastic Regular Expressions}
\label{sec:sre}
To characterize the likely lenses, we must compute the expected number of bits
needed to recover a string in one data source from a synchronized string in the
other data source. To do this, we must first develop a probabilistic language
model for our language. We do this with \emph{stochastic regular expressions},
regular expressions annotated with probability information. With this, we can
jointly express a language and a probability distribution over that language. In
the following grammar, $\String$ ranges over strings, and $\Probability$ ranges
over real numbers between 0 and 1, exclusive.

@@

@@

\paragraph*{Information-Theoretic Cost Metric}
Instead of searching for \emph{any} term that satisfies the specification, we
search for the \emph{best} term that satisfies the specification. This begs the
question: what metric should we use to determine which term is best?
Intuitively, we aim to synthesize the lens which is ``closest'' to being a
bijection. Somewhat more formally, we aim to synthesize a lens which minimizes
the expected number of bits which must be used to recover the source from the
target, and the target from the source.
